---
title: "Team"
author: "Kenneth Mendoza"
date: "November 13, 2019"
output: html_document
---
***

**Processing Data**
```{r data}
library(ggplot2)
library(tidyr)
library(dplyr)
df = read.table('diabetes.txt',header=TRUE)
df$frame = droplevels(df$frame,"")

df$frame= as.character(df$frame)
df = subset(df, select = -c(1, 15:16))
diabetes_clean = na.omit(df)
df$frame[is.na(df$frame)] = 'NA'
df$frame = as.factor(df$frame)

diabetes_reduced = subset(df, select = -c(1, 15:16))

is.na(diabetes_clean)
```
By using is.na, we can check if all na values were dropped from the data set. All values should show as FALSE since there are no na values in "diabetes_clean"

***

**Exploring and transforming data**
```{r plot}
summary(diabetes_clean$glyhb)
as.factor(diabetes_clean$glyhb)
diabetes_clean$glyhb_star[diabetes_clean$glyhb<4.4] = 1
diabetes_clean$glyhb_star[diabetes_clean$glyhb>=4.4 & diabetes_clean$glyhb <4.9 ] = 2
diabetes_clean$glyhb_star[diabetes_clean$glyhb>=4.9 & diabetes_clean$glyhb <5.7 ] = 3
diabetes_clean$glyhb_star[diabetes_clean$glyhb>5.7 & diabetes_clean$glyhb <17 ] = 4
ggplot(diabetes_clean, aes(glyhb_star)) + geom_histogram()
diabetes_clean %>% group_by(frame) %>% summarise(mean.glyhb = mean(glyhb_star))
```
Glyhb was fixed by turning it into a factor and separating levels based on the 5 number summary. Some downsides to the approach are that the levels of factors are not equally distributed, this was done so that the histogram is symmetrical.

***

**Gather and Spread**

The Gather command reshapes data from a wide format to a long format. The Spread command does the opposite, reshaping data from a long format to a wide format. This makes the 2 commands complements of each other since they are inversely proportionate.
